Beam-Helicity and Beam-Charge Asymmetries \\ in the \red{DVCS and Bethe--Heitler processes} on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.3)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-20 background_and_systematic_dual.tex
Version 2.3
Version 2.3 with correct abbrevs.

The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in Table~\ref{table_systematic_contributions_0607}.

The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period. These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c||c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{\red{The values of the asymmetries extracted in a single bin over the entire kinematic range with their statistical uncertainties are presented in the second column of this table. The third, fourth and fifth columns show t}he contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}. The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period. These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c||c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{\red{The values of the asymmetries extracted in a single bin over the entire kinematic range with their statistical uncertainties are presented in the second column of this table. The third, fourth and fifth columns show t}he contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2012-01-20 experiment_and_data.tex
Version 2.3 with correct abbrevs.

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ receives a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
which is bilinear in CFFs. However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}. As a result of the more complicated dependence on the CFFs and this suppression, it
is more difficult to constrain GPDs via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the kinematically-unsuppressed leading twist amplitudes.

>>>>

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ receives a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
which is bilinear in CFFs. However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}. As a result of the more complicated dependence on the CFFs and this suppression, it
is more difficult to constrain GPDs via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the kinematically-unsuppressed leading twist amplitudes.

### 2012-01-20 results_dual.tex
Version 2.3 with correct abbrevs.

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}. The results from this paper will be made available in the Durham Database\red{. The results will also be made} available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.

>>>>

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}. The results from this paper will be made available in the Durham Database\red{. The results will also be made} available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.

### 2012-01-20 theory.tex
Version 2.3 with correct abbrevs.

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon. A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton \red{densitie}s~\cite{Bur00}. \red{The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels. Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive physics processes. In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see fig.~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon. A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton \red{densitie}s~\cite{Bur00}. \red{The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels. Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive physics processes. In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}
